---
title: "Analysis - exp1"
author: "Alex Holcombe, Filip Děchtěrenko, "
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


## Load data and libraries

Load data from the experiment

```{r load data and libraries, warning = F, message = F}
set.seed(191124)
library(tidyverse); theme_set(theme_classic(16))
library(lme4)
library(here)

source(here("R","utils.R"))

plots_dir <- here("plots", "exp1")

if(!dir.exists(plots_dir)) {
  dir.create(plots_dir)
}

#I'm thinking something else has to create the rds file first
df <- read_rds(here::here("data", "exp1", "data_191129.rds"))

df_participants <- readxl::read_excel(here("data","exp1","participant_exp1_complete.xlsx"))

```

## Filter participants with low accuaracy

```{r filter low accuracy in normal MOT}
df_bad <- df %>% filter(t_contr == "MOT") %>% group_by(subject_id) %>% summarize(m = mean(acc)) %>% filter(m <0.75)
```

Luckily, we did not need to filter anyone

## Descriptive statistics

```{r simple desc stat}
df_participants %>% summarize(n = n())
df %>% group_by(t_contr) %>% summarize(m = mean(acc), sd = sd(acc))
df %>% group_by(t_contr,mark_type) %>% summarize(m = mean(acc), sd = sd(acc))
```

## Visualize

```{visualize results}

p <- df %>% 
  group_by(subject_id, t_contr,mark_type) %>% 
  filter(t_contr == "MOT") %>% 
  summarize(nCorrect = mean(nCorrect, na.rm = T)) %>% 
  ggplot(aes(x = t_contr, y = nCorrect,col = mark_type)) + 
  stat_summary(fun.data="mean_cl_boot") + 
  theme(aspect.ratio = 1) + 
  ylim(0,4) + 
  ggtitle("Number of correctly selected targets") + 
  xlab("contrast level") + 
  ylab("# targets")
p
ggsave(file.path(plots_dir, sprintf("exp1_results_noleg.svg")), plot = p + theme(legend.position = "none"),width = 6, height = 6)
ggsave(file.path(plots_dir, sprintf("exp1_results.svg")), plot = p,width = 6, height = 6)

```

## Test

```{test lmer}
lm1    <- glmer(acc~t_contr+(1|subject_id), data = df %>% filter(t_contr != "MOT"), family= "binomial")
lm1null <- glmer(acc~1+(1|subject_id), data = df %>% filter(t_contr != "MOT"), family= "binomial")
anova(lm1, lm1null)
```

```{test lmer mark}
df_noise <- df %>% filter(t_contr != "MOT")

lm2_full    <- glmer(acc~t_contr*mark_type+(1|subject_id)+(1|trajectory_id), data = df_noise, family= "quasibinomial")
lm2_noint    <- glmer(acc~t_contr+mark_type+(1|subject_id)+(1|trajectory_id), data = df_noise, family= "binomial")

lm2_noint_REML    <- glmer(acc~t_contr+mark_type+(1|subject_id)+(1|trajectory_id), data = df_noise, family= "binomial", REML = T)
lm2_noint_notraj_id    <- glmer(acc~t_contr+mark_type+(1|subject_id), data = df_noise, family= "binomial", REML = T)
lm2_noint_nosubj_id    <- glmer(acc~t_contr+mark_type+(1|trajectory_id), data = df_noise, family= "binomial", REML = T)

lm2_justmark    <- glmer(acc~mark_type+(1|subject_id)+(1|trajectory_id), data = df_noise, family= "binomial")
lm2_justcontr    <- glmer(acc~t_contr+(1|subject_id)+(1|trajectory_id), data = df_noise, family= "binomial")


lm2_null <- glmer(acc~1+(1|subject_id)+(1|trajectory_id), data = df %>% filter(t_contr != "MOT"), family= "binomial")
anova(lm2_noint_notraj_id, lm2_noint_REML)
anova(lm2_noint_nosubj_id, lm2_noint_REML)

anova(lm2_full, lm2_noint)
anova(lm2_null, lm2_justmark)
anova(lm2_null, lm2_justcontr)
anova(lm2_noint, lm2_justcontr)
anova(lm2_noint, lm2_justmark)
```

### Compute effect size per each individual contrast level

We are averaging data per each subject, contrast level and mark type. This inflates the CI, but the estimate should be correct.

```{r effect size per contrast}
df1 <- df %>% 
  filter(t_contr != "MOT") %>% 
  group_by(t_contr,subject_id,mark_type) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  group_by(t_contr) %>% 
  do(dc = effsize::cohen.d(nCorrect~mark_type,.,paired=T)$estimate,
     dc_CI = effsize::cohen.d(nCorrect~mark_type,.,paired=T)$conf.int,
     c = cor(.$nCorrect[.$mark_type == "mark"],.$nCorrect[.$mark_type == "noMark"]),
     tt = t.test(nCorrect~mark_type, ., paired = T)) 

df1 %>% 
  mutate(d = unlist(dc), d_low = unlist(dc_CI)[1], d_high = unlist(dc_CI)[2], c = unlist(c),
         tt)

```

```{r effect size between contrasts}
df_13 <- df %>% 
  filter(t_contr %in% c("1","3")) %>% 
  group_by(t_contr,subject_id) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  ungroup() %>% 
  do(dc = effsize::cohen.d(nCorrect~t_contr,.,paired=T)$estimate %>% unlist(),
     dc_CI = effsize::cohen.d(nCorrect~t_contr,.,paired=T)$conf.int,
     c = cor(.$nCorrect[.$t_contr == "1"],.$nCorrect[.$t_contr == "3"]),
     tt = t.test(nCorrect~t_contr, ., paired = T)) 
df_13 %>% 
  mutate(d = unlist(dc), d_low = unlist(dc_CI)[1], d_high = unlist(dc_CI)[2], c = unlist(c),
         tt)

```

## Difference between MOT and high contrast noise mot

Pretty obvious, but it is in preregistration.

```{r normal mot - noise mot difference}
df %>% 
  filter(t_contr %in% c("3","MOT")) %>% 
  group_by(subject_id,t_contr) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  t.test(nCorrect~t_contr,., var.equal = T)

rbind(df %>% 
  filter(t_contr %in% c("3","MOT")) %>% 
  group_by(subject_id,t_contr) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  spread(t_contr,nCorrect) %>% 
  cor.test(~`3`+MOT,.) %>% broom::tidy(),

df %>% 
  filter(t_contr %in% c("2","MOT")) %>% 
  group_by(subject_id,t_contr) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  spread(t_contr,nCorrect) %>% 
  cor.test(~`2`+MOT,.)%>% broom::tidy(),

df %>% 
  filter(t_contr %in% c("1","MOT")) %>% 
  group_by(subject_id,t_contr) %>% 
  summarize(nCorrect = mean(nCorrect)) %>% 
  spread(t_contr,nCorrect) %>% 
  cor.test(~`1`+MOT,.)%>% broom::tidy()) %>% 
  pull(estimate) %>% range() %>% round(2)
```

## Differences in trajectories


